Covariate analysis of ROSMAP reprocessed counts (with CQN normalisation and covariates adjusted)

### 2017-04-06 code/Rmd/ROSMAP_REPROCESSED.Rmd

# Get residuals from differential expression model
RESIDUAL.SVA.GENE_EXPRESSION = residuals.MArrayLM(FIT, VOOM.WEIGHTS$E)

@@

# Plot variance components
var.comp = data.frame(component = 1:length(actual.var), 
                      residual = actual.var, 
                      permuted.residual = permuted.var) %>%
  tidyr::gather(data, value, -component)
p = ggplot(var.comp %>% filter(component <= 10), aes(x = component, y = value, color = data)) + geom_point()
p = p + geom_hline(yintercept=permuted.var[1], linetype = 'dashed') + xlab('Singular Dimension Index')
p = p + geom_vline(xintercept=NUM.SV, linetype = 'dashed') + ylab('Fraction of Variance Explained')
p = p + theme(legend.position = c(0.8, 0.8), legend.title = element_blank())
p

>>>>

# Get residuals from differential expression model
RESIDUAL.SVA.GENE_EXPRESSION = residuals.MArrayLM(FIT, CQN.GENE_EXPRESSION$y+CQN.GENE_EXPRESSION$offset)

@@

# Plot variance components
var.comp = data.frame(component = 1:length(actual.var), 
                      residual = actual.var, 
                      permuted.residual = permuted.var) %>%
  tidyr::gather(data, value, -component)
p = ggplot(var.comp %>% filter(component <= round(NUM.SV*1.3)), aes(x = component, y = value, color = data)) + geom_point()
p = p + geom_hline(yintercept=permuted.var[1], linetype = 'dashed') + xlab('Singular Dimension Index')
p = p + geom_vline(xintercept=NUM.SV, linetype = 'dashed') + ylab('Fraction of Variance Explained')
p = p + theme(legend.position = c(0.8, 0.8), legend.title = element_blank())
p
